[Re] Chaos in a long-term experiment with a plankton community

### 2016-02-12 article/article.tex
latest build of article pdf

@@

Reproduced divergence rates (figure \ref{fig:divergence}) and Lyapunov
exponents (figure \ref{fig:LE_comparison}) were somewhat different from
those in the original article.. The original article states: ``the
distance between initially nearby trajectories increased over time, and
reached a plateau after about 20--30 days''. The reproduced results
appear not inconsistent with this statement, except for one group of
species (Harpacticoids). The original article also stated that the
analyses ``yielded significantly positive Lyapunov exponents of
strikingly similar value for all species (Fig. 3; mean exponent = 0.057
per day, s.d. = 0.005 per day, n = 9)''. Reproduced exponents had very
similar mean value, but had much larger standard deviation (mean = 0.057
and s.d. = 0.014).

@@

Considerable quantitative difference in predictability decay
(\ref{fig:prediction_distance}) remain unexplained.

>>>>

\section{Draft article}\label{draft-article}

@@

Reproduced divergence rates (figure \ref{fig:divergence}) and Lyapunov
exponents (figure \ref{fig:LE_comparison}) were somewhat different from
those in the original article.. The original article states: ``the
distance between initially nearby trajectories increased over time, and
reached a plateau after about 20--30 days''. The reproduced results
appear not inconsistent with this statement, except for one group of
species (Harpacticoids). The original article also stated that the
analyses ``yielded significantly positive Lyapunov exponents of
strikingly similar value for all species (Fig. 3; mean exponent = 0.057
per day, s.d. = 0.005 per day, n = 9)''. Reproduced exponents had very
similar mean value, but had much larger standard deviation (mean = 0.060
and s.d. = 0.014).

@@

Considerable quantitative difference in predictability decay
(\ref{fig:prediction_distance}) remain unexplained, though could result
from original analyses using neural networks, and the reproduction using
GAMs.
